---
title: "Honors Thesis: Mental Health Among Meredith College Students"
author: "Sarah Halsey"
date: "3/17/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Beginnings
Here, I am installing various packages necessary to complete this project. Packages include tidyverse,...
I am also reading in the survey data, titling it 'survey'.

```{r install-packages, echo = FALSE, message = FALSE, include=FALSE}
# install.packages("tidyverse")
library(tidyverse)
library(tidymodels)
library(caret)
library(dplyr)
library(ggplot2)
library(ggridges)
library(naniar)
```

```{r reading-in-data, echo=FALSE, message=FALSE, include=FALSE}
survey <- read_csv("Mental Health Among Collegiate Athletes2.csv")
glimpse(survey)
```



## Data Wrangling

We also need to rename the variables to make them easier to work with. 
Variables needed to clean up:
*Are you on an athletic team? --> athlete
*Major(or intended, if not yet declared) --> major1
*Are you obtaining a Bachelors of Science or Bachelors of Arts for Major? --> degree1
*Second Major(if applicable) --> major2
*Are you obtaining a Bachelors of Science or Bachelors of Arts for Major#2? --> degree2
*Cumulative GPA (Round to 2 decimal places) --> cumgpa
*Major GPA (Round to 2 decimal places) --> majorgpa

```{r renaming-variables}
survey1 <- survey %>%
  rename(athlete = `Are you on an athletic team at Meredith College?`,
         major1 = `Major (or intended, if not yet declared)`,
         degree1 = `Are you obtaining a Bachelors of Arts or Bachelors of Science for Major?`,
         major2 =  `Second Major (if applicable)`,
         degree2 = `Are you obtaining a Bachelors of Arts or Bachelors of Science for Major #2? (if applicable)`,
         cumgpa = `Cumulative GPA (round to 2 decimal places)`,
         majorgpa = `Major GPA (round to 2 decimal places)`)
```

*Anxiety Symptoms:
- Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Numbness or tingling] --> numbting

-Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Feeling hot] --> hot

-Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Wobbliness in legs] --> wobble

-Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Unable to relax] --> norelax

-same format for rest of anxiety symptoms


```{r renaming-anxiety-symptoms}
survey1 <- survey1 %>%
  rename(numbting = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Numbness or tingling]`,
         hot = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Feeling hot]`,
         wobble = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Wobbliness in legs]`,
         norelax = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Unable to relax]`,
         fear_worst = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Fear of worst happening]`,
         dizzy_light = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Dizzy or lightheadeed]`,
         heart_race = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Heart pounding / racing]`,
         unsteady = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Unsteady]`,
         afraid = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Terrified or afraid]`,
         nervous = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Nervous]`,
         choking = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Feeling of choking]`,
         hands_tremble = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Hands trembling]`,
         shaky = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Shaky / unsteady]`,
         fear_control = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Fear of losing control]`,
         diff_breath = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Difficulty in breathing]`,
         fear_dying = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Fear of dying]`,
         scared = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Scared]`,
         indigest =  `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Indigestion]`,
         faint = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Faint / lightheaded]`,
         face_flush = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Face flushed]`,
         sweats = `Please check the symptoms you have experienced within this past school year (starting in August 2021) due to anxiety (Beck Anxiety Inventory). | Select the severity of each symptom: 0 (not severe), 1 (mild), 2 (moderately), 3 (severe) [Hot / cold sweats]`)

```

```{r remove-first-2-columns}
survey1 <- subset(survey1, select = -c(`Timestamp`, `Participant’s Online DECISION:If you choose NOT to participate, please close your browser at this time.If you choose to participate in this research study, please read the statement below and indicate your consent by checking the box and submitting your response. You will then be taken to the survey. Before submitting, please print a copy of this consent page for your records.`))

```

creating new variable that sums all of anxiety symptoms

```{r  total-anxiety}
survey1$anxiety_total = rowSums(survey1[c(9:29)])
view(survey1)
```


Renaming rest of the variables:

```{r renaming-rest-of-variables}
survey1 <- survey1 %>%
  rename(seek_help = `Would you seek help for anxiety?`,
         years_college_sport = `How many years have you been a collegiate athlete?`,
         freq_play = `Based on your frequency of participating, how would you classify your status in your sport?`,
         years_sport = `How long have you been playing your sport competitively? (Please just type number of years)`,
         concussion = `How many times have you had a concussion? (if any)`)
```



We need to clean up some of this data, including making variables binary. The variables we are making binary are as follows:
*athlete  --> no = 0, yes = 1
*degree1 --> BA = 0, BS = 1
*degree2--> BA = 0, BS = 1
*concussion --> 0 = 1, 1,2,3,4,5+ = 1

```{r binary-variables-athlete}
survey1<- survey1 %>%
    mutate(athlete = case_when(athlete == "Yes" ~ "1",
                              athlete == "No" ~ "0"),
           athlete = as.factor(athlete))
```

```{r binary-variables-degree1}
survey1<- survey1 %>%
  mutate(degree1 = case_when(degree1 == "Bachelors of Science" ~ "1",
                              degree1 == "Bachelors of Arts" ~ "0"),
           degree1 = as.factor(degree1))
```

```{r binary-variables-degree2}
survey1<- survey1 %>%
  mutate(degree2 = case_when(degree2 == "Bachelors of Science" ~ "1",
                              degree2 == "Bachelors of Arts" ~ "0"),
           degree2 = as.factor(degree2))
```

```{r binary-variables-concussion}
survey1<- survey1 %>%
  mutate(concussion = case_when(concussion == "1" ~ "1",
                                concussion == "2" ~ "1",
                                concussion == "3" ~ "1",
                                concussion == "4" ~ "1",
                                concussion == "5+" ~ "1",
                                concussion == "0" ~ "0"),
         concussion = as.factor(concussion))
```


## Categorizing Variables

Need to categorize major, GPA, anxiety_total, and sport (team vs. individual)
- Major is by overall department, per Meredith College.
- GPA categories 
- Anxiety total levels based on Beck Anxiety Inventory
    - 0 - 21 --> "0"
    - 22 - 63 --> "1"

```{r categorizing major}
survey1 <- survey1 %>%
  mutate(major_group = case_when(major1 == "Art Education" ~ "Arts & Humanities",
                               major1 == "Graphic Design"  ~ "Arts & Humanities",
                               major1 == "Studio Art" ~ "Arts & Humanities",
                               major1 == "Communication" ~ "Arts & Humanities",
                               major1 == "Communications" ~ "Arts & Humanities",
                               major1 == "Dance" ~ "Arts & Humanities",
                               major1 == "Dance Education" ~ "Arts & Humanities",
                               major1 == "Theatre" ~ "Arts & Humanities",
                               major1 == "English" ~ "Arts & Humanities",
                               major1 == "History" ~ "Arts & Humanities",
                               major1 == "International Studies" ~ "Arts & Humanities",
                               major1 == "Political Science" ~ "Arts & Humanities",
                               major1 == "Music" ~ "Arts & Humanities",
                               major1 == "Music Education" ~ "Arts & Humanities",
                               major1 == "Religious & Ethical Studies" ~ "Arts & Humanities",
                               major1 == "Criminology" ~ "Arts & Humanities",
                               major1 == "Sociology" ~ "Arts & Humanities",
                               major1 == "Spanish" ~ "Arts & Humanities",
                               major1 == "Business Administration" ~ "Business",
                               major1 == "Business" ~ "Business",
                               major1 == "Economics" ~ "Business",
                               major1 == "Hospitality & Tourism Management" ~ "Business",
                               major1 == "Education" ~ "Education, Health, & Human Sciences",
                               major1 == "Child Development" ~ "Education, Health, & Human Sciences",
                               major1 == "Family & Consumer Sciences" ~ "Education, Health, & Human Sciences",
                               major1 == "Fashion Merchandising & Design" ~ "Education, Health, & Human Sciences",
                               major1 == "Interior Design" ~ "Education, Health, & Human Sciences",
                               major1 == "Exercise & Sports Science" ~ "Education, Health, & Human Sciences",
                               major1 == "Exercise Sports & Science" ~ "Education, Health, & Human Sciences",
                               major1 == "Food & Nutrition" ~ "Education, Health, & Human Sciences",
                               major1 == "Psychology" ~ "Education, Health, & Human Sciences",
                               major1 == "Social Work" ~ "Education, Health, & Human Sciences",
                               major1 == "Biology" ~ "Natural & Mathematical Sciences",
                               major1 == "Environmental Sustainability" ~ "Natural & Mathematical Sciences",
                               major1 == "Public Health" ~ "Natural & Mathematical Sciences",
                               major1 == "Chemistry" ~ "Natural & Mathematical Sciences",
                               major1 == "Computer Science" ~ "Natural & Mathematical Sciences",
                               major1 == "Mathematics" ~ "Natural & Mathematical Sciences",
                               major1 == "Engineering" ~ "Natural & Mathematical Sciences"))
```

```{r dropping-graduates}
survey1 <- subset(survey1, major_group == "Arts & Humanities" | major_group == "Business" | major_group == "Education, Health, & Human Sciences" | major_group == "Natural & Mathematical Sciences")

view(survey1)
```


```{r categorizing-gpa}
#survey1 <- survey1 %>%
  #mutate(gpa_group = case_when(cumgpa >= 3.7 ~ "3.7 - 4.0",
                               #cumgpa >= 3.4 ~ "3.4 - 3.7",
                               #cumgpa >= 3.0 ~ "3.0 - 3.4",
                               #cumgpa >= 2.5 ~ "2.5 - 3.0",
                               #TRUE ~ "below 2.5"))
```

```{r replacing-83}
survey1 <- 
  survey1 %>% replace_with_na(replace = list(cumgpa = "Transfer student, no gpa yet"))
```

```{r making-cumgpa-numeric}
survey1$cumgpa <- as.numeric(as.character(survey1$cumgpa))  
```

```{r categorizing-gpa2}
survey1 <- survey1 %>%
  mutate(gpa_group = case_when(cumgpa < 2.5 ~ "below 2.5",
                                cumgpa >= 2.5 & cumgpa < 3.0 ~ "2.5 - 3.0",
                                cumgpa >= 3.0 & cumgpa < 3.4 ~ "3.0 - 3.4",
                                cumgpa >= 3.4 & cumgpa < 3.7 ~ "3.4 - 3.7",
                                cumgpa >= 3.7 ~ "3.7 - 4.0"))
```

```{r test}
test <-
survey1 %>%
filter_at(vars(starts_with("gpa_group2")), any_vars(is.na(.)))
view(test)
```


According to Beck Anxiety Inventory, those who have a score of 0-21 indicates very low anxiety. Those in the range of 22-35 have moderate anxiety, and those who have a sum of over 36 indicates severe anxiety.
In order to make this variable binary, I collapsed the moderate and severe anxiety group into one group. Those who have a range of 22-63 would be designtated with 1, while those with less than 22 would be given a 0.

```{r making-anxiety_total-binary }
survey1 <- survey1 %>%
  mutate(anxiety_total_level = case_when(anxiety_total >= 22 ~ "1",
                                        TRUE ~ "0"),
                  anxiety_total_level = as.factor(anxiety_total_level))
view(survey1)
```


We then categorize sport. If it is a team sport or individual. 
Team Sports: Basketball, Softball, Soccer, Volleyball, Lacrosse, Field Hockey --> will be distinguished with a 1
Individual: Golf, Track & Field, Cross Country, Tennis --> will be distinguished with a  0

```{r cateogorizing-binary-sport}
survey1 <- survey1 %>%
  mutate(sport_group = case_when(Sport == "Basketball" ~ "1",
                                 Sport == "Softball" ~ "1",
                                 Sport == "Soccer" ~ "1",
                                 Sport == "Volleyball" ~ "1",
                                 Sport == "Lacrosse" ~ "1",
                                 Sport == "Field Hockey" ~ "1",
                                 Sport == "Golf" ~ "0",
                                 Sport == "Track & Field" ~ "0",
                                 Sport == "Cross Country" ~ "0",
                                 Sport == "Tennis" ~ "0"))

view(survey1)
```


## Early Data Analysis (Visuals)

See how many athletes/nonathletes responded. We also see how many people from each sport responded. 
```{r visual-athletes  vs. nonathletes}
ggplot(data = survey1, aes(x = athlete)) +
  geom_histogram(stat = "count")

survey1 %>%
  filter(athlete == "1") %>%
  ggplot(aes(x=athlete)) + geom_histogram(stat="count") + facet_wrap(~Sport)
```

Distribution of total_anxiety score
```{r distribution-anxiety_total}
ggplot(data = survey1, aes(x=anxiety_total)) +
  geom_bar()
```

Boxplot of athlete vs. total anxiety score & summary stats
```{r boxplot-anxiety_total-athlete-and-summary_stats}

plot(survey1$athlete, survey1$anxiety_total)

tapply(survey1$anxiety_total, survey1$athlete, summary)
```
Boxplot of whether you have had a concussion and total anxiety score
```{r boxplot-concussion-anxiety_total}
plot(survey1$concussion, survey1$anxiety_total)
```


Boxplot of year and anxiety total
```{r boxplot-year-anxiety_total}
survey1 %>%
  filter(Year == "Freshman" | Year == "Junior" | Year == "Sophomore" | Year == "Senior") %>%
ggplot(aes(x = Year, y=anxiety_total)) +
  geom_boxplot()
```

Boxplot of anxiety_total by gpa_group
```{r boxplot-anxiety_total-gpa_group}
ggplot(data = survey1, aes(y = anxiety_total, color = gpa_group)) + geom_boxplot() + labs(y = "Total Anxiety Score", title = "Distribution of Total Anxiety Score", subtitle = "By GPA", color = "GPA Range") + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
```
Density curve of anxiety_total
```{r density-anxiety_total}
ggplot(data = survey1, aes(x = anxiety_total)) +
  geom_density()
```
Density curve of anxiety_total by GPA group
```{r density-anxiety_total-gpa_group}
ggplot(data = survey1, 
       mapping = aes(x = anxiety_total, 
                     color = gpa_group)) +
  geom_density()
```


Density curve of anxiety_total by major_group
```{r density-anxiety_total-major_group}
ggplot(data = survey1, 
       mapping = aes(x = anxiety_total,
                     color = major_group)) +
  geom_density()
```



```{r boxplot-anxiety_total-major_group}
ggplot(data = survey1, mapping = aes(y = anxiety_total, color = major_group)) +
  geom_boxplot() +  labs(y = "Anxiety Total Score ", title = "Distribution of  Anxiety", subtitle  = "By Academic Department", color = "Department")  + theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
```


## Official Visuals

# BoxPlots

```{r releveling-gpa_group}
survey1$gpa_group = factor(survey1$gpa_group, levels=c("below 2.5", "2.5-3.0", "3.0-3.4", "3.4-3.7", "3.7-4.0"))
```

```{r boxplot-anxiety_total-gpa_group}
ggplot(data = survey1, aes(x = gpa_group, y = anxiety_total, color = gpa_group)) + geom_boxplot() + labs(x = "GPA Range", y = "Total Anxiety Score", title = "Distribution of Total Anxiety Score", subtitle = "By GPA", color = "GPA Range")
  
  #scale_x_discrete(limits = rev(levels(survey1$gpa_group2)))
  
  #theme(axis.text.x = element_blank(), axis.ticks.x = element_blank())
```






# Stacked Bar Charts
```{r anxiety-prevelance_athlete}
survey1 %>%
  filter(athlete =="1" | athlete =="0") %>%
  ggplot(aes(x = athlete, fill = anxiety_total_level)) +
  geom_bar(position = "fill") +
  labs(
    x = 'Athlete', 
    fill = "Anxiety Prevelance", 
    y = NULL,
    title = 'Anxiety Prevelance', subtitle = 'By Athletic Distinction'
    ) +
  scale_fill_manual(values = c("#DEB4A0", "#CA235F"))
```

```{r re-factoring-Department}
survey1$major_group = factor(survey1$major_group, levels=c("Arts & Humanities", "Education, Health, & Human Sciences", "Business", "Natural & Mathematical Sciences"))
```

```{r  anxiety-prevelance_department}
survey1 %>%
  filter(major_group =="Arts & Humanities" | major_group == "Business" | major_group == "Education, Health, & Human Sciences" | major_group == "Natural & Mathematical Sciences") %>%
  ggplot(aes(x = major_group, fill = anxiety_total_level)) +
  geom_bar(position = "fill") +
  labs(
    x = 'Department', 
    fill = "Anxiety Prevelance", 
    y = NULL,
    title = 'Anxiety Prevelance', subtitle = 'By Academic Department'
    ) + theme(axis.text.x = element_text(size = 8, angle = 10)) + scale_fill_manual(values = c("#DEB4A0", "#CA235F"))
```


```{r re-factoring-Year}
survey1$Year = factor(survey1$Year, levels=c("Freshman", "Sophomore", "Junior", "Senior"))
```


```{r anxiety-prevelance_class-year}
survey1 %>%
  filter(Year == "Freshman" | Year == "Sophomore" | Year == "Junior" | Year == "Senior") %>%
  ggplot(aes(x = Year, fill = anxiety_total_level)) +
  geom_bar(position = "fill") +
  labs(
    x = 'Year', 
    fill = "Anxiety Prevelance", 
    y = NULL,
    title = 'Prevelance of Anxiety', subtitle = 'By Class Year'
    ) +
  scale_fill_manual(values = c("#DEB4A0", "#CA235F"))
```

```{r plot3}
survey1 %>%
  filter(gpa_group == "below 2.5" | gpa_group == "2.5 - 3.0" | gpa_group == "3.0 - 3.4" | gpa_group == "3.4 - 3.7" | gpa_group == "3.7 - 4.0") %>%
  ggplot(aes(x = gpa_group, fill = anxiety_total_level)) +
  geom_bar(position = "fill") +
  labs(
    x = 'GPA', 
    fill = "Anxiety Prevelance", 
    y = NULL,
    title = 'Prevelance of Anxiety', subtitle = 'By Class Year'
    ) +
  scale_fill_manual(values = c("#DEB4A0", "#CA235F"))
```


```{r gpa-anxiety_total}
survey1 %>%
  ggplot(aes(x = gpa_group, y = anxiety_total_level, fill = anxiety_total_level, color = anxiety_total_level)) +
  geom_density_ridges2(alpha = 0.5) +
  labs(
    x = "Number of characters (in thousands)", 
    y = "Spam",
    title = "Spam vs. number of characters"
    ) +
  guides(color = FALSE, fill = FALSE) +
  scale_fill_manual(values = c("#E48957", "#CA235F")) +
  scale_color_manual(values = c("#DEB4A0", "#CA235F"))
```

## Logistic Regression

```{r creating-new-data-fram}
survey2 <- survey1 %>%
  select(Year, athlete, major_group, cumgpa, anxiety_total_level, gpa_group2) %>%
  drop_na()
```

```{r splitting-data-driveers, echo=FALSE, include=FALSE}
set.seed(1234)
survey1_split <- initial_split(survey1, prop = 0.80)
survey1_train <- training(survey1_split)
survey1_test <- testing(survey1_split)
```

```{r logisitic-regression}
anxiety_fit <- glm(anxiety_total_level ~ gpa_group + major_group + athlete + Year, data = survey1, family = "binomial")

tidy(anxiety_fit)
```

```{r confusion-matrix}
pred_train <- predict(anxiety_fit, survey1_train, type = "response")
#Calculate predicted 0/1 values for the  injury variable using a threshold of 0.5:
pred_num <- ifelse(pred_train > 0.5, 1, 0)
pred_num <- factor(pred_num, levels = c(0,1))
confusionMatrix(pred_num, survey1_train$anxiety_total_level)
```

```{r ROC-curve}
anxiety_pred <- as_tibble(pred_train)

anxiety_pred %>%
  roc_curve(
    truth = survey1_train$anxiety_total_level,
    value,
    event_level = "second") %>%
  autoplot()

anxiety_pred %>%
  roc_auc(
    truth = survey1_train$anxiety_total_level,
    value,
    event_level = "second"
  )
```










